On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-10 Manuscript/manuscript.tex
citation for R

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x = 1$, the standard deviation of $X_t$; and
3) $\phi$, the lag-1 autocorrelation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
10,000 replicates. The 
block bootstrap sampling step was done with function \texttt{tsboot} from R 
package \textsl{boot},\citep{boot} with block size $\lceil n / l \rceil$. This 
function by default is an implementation of moving block bootstrap as described 
in the previous section, meaning that that blocks are allowed to wrap around, 
and we tried both $l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$,
keeping the order of the block size constant but varying the coefficient. 
For each replicate, we constructed 
six 95\% block bootstrap 
CIs for each parameter as described in the last section with $B = 1000$. We can
estimate $\mu$, $\sigma_x$, and $\phi$ by computing the sample mean,
sample standard deviation, 
and lag-1 autocorrelation, respectively, of each bootstrap sample. Then we can 
construct intervals for each parameter using the appropriate procedures 
described in \textit{Block Bootstrap CIs}. 
Then we estimated their actual coverage 
rates along with their 95\% confidence intervals from the 10,000 replicates.

>>>>

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x = 1$, the standard deviation of $X_t$; and
3) $\phi$, the lag-1 autocorrelation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
10,000 replicates. The 
block bootstrap sampling step was done with function \texttt{tsboot} from R 
\citep{R}
package \textsl{boot},\citep{boot} with block size $\lceil n / l \rceil$. This 
function by default is an implementation of moving block bootstrap as described 
in the previous section, meaning that that blocks are allowed to wrap around, 
and we tried both $l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$,
keeping the order of the block size constant but varying the coefficient. 
For each replicate, we constructed 
six 95\% block bootstrap 
CIs for each parameter as described in the last section with $B = 1000$. We can
estimate $\mu$, $\sigma_x$, and $\phi$ by computing the sample mean,
sample standard deviation, 
and lag-1 autocorrelation, respectively, of each bootstrap sample. Then we can 
construct intervals for each parameter using the appropriate procedures 
described in \textit{Block Bootstrap CIs}. 
Then we estimated their actual coverage 
rates along with their 95\% confidence intervals from the 10,000 replicates.
